Pushdown Control-Flow Analysis via Refunctionalization (Functional Pearl)

### 2018-02-27 paper.tex
update

As we mentioned previously, the space of addresses is finite in AAM.
Binding addresses are parameterized by variable names and the time that creates this binding,
which are both finite.
Continuation addresses @KAddr@ has two variants: 
1) @Halt@ which corresponds to the empty stack, and
2) @ContAddr@ consists of the entry expression of callee and the time that
creates this address, and they are also finite. 
(TODO: why target expression, allocation polyvariance)

@@

abstract class KAddr
case object Halt extends KAddr
case class ContAddr(tgt: Expr, time: Time) extends KAddr
\end{lstlisting}

@@

\begin{lstlisting}
def allocBind(x: String, time: Time): BAddr = BAddr(x, time)
def allocKont(tgtExpr: Expr, time: Time): KAddr = ContAddr(tgtExpr, time)
\end{lstlisting}

@@

\begin{lstlisting}
def step(s: State): List[State] = {
  val new_time = tick(s)
  s match {
    case State(Let(x, App(f, ae), e), env, bstore, kstore, kaddr, time) 
      if isAtomic(ae) =>
      val closures = atomicEval(f, env, bstore).toList
      for (Clos(Lam(v, body), env_c) <- closures) yield {
        val baddr = allocBind(v, new_time)
        val new_env = env_c + (v -> baddr)
        val new_bstore = bstore.update(baddr, atomicEval(ae, env, bstore))
        val new_kaddr = allocKont(body, new_time)
        val new_kstore = kstore.update(new_kaddr, Cont(Frame(x, e, env), kaddr))
        State(body, new_env, new_bstore, new_kstore, new_kaddr, new_time)
      }
    case State(ae, env, bstore, kstore, kaddr, time) 
      if isAtomic(ae) =>
      val conts = kstore(kaddr).toList
      for (Cont(Frame(x, e, env_f), f_kaddr) <- conts) yield {
        val baddr = allocBind(x, new_time)
        val new_env = env_f + (x -> baddr)
        val new_store = bstore.update(baddr, atomicEval(ae, env, bstore))
        State(e, new_env, new_store, kstore, f_kaddr, new_time)
      }
  }
}
\end{lstlisting}

@@

\begin{lstlisting}
case class P4FContAddr(tgt: Expr, tgtEnv: Env, time: Time) extends KAddr
def allocKont(tgtExpr: Expr, tgtEnv: Env, time: Time): KAddr = 
  P4FContAddr(tgtExpr, tgtEnv, time)
\end{lstlisting}

@@

\begin{lstlisting}
case class Config(e: Expr, env: Env, store: BStore, time: Time)
case class ValStore(vs: Set[Storable], store: BStore, time: Time)
type Cache = Map[Config, ValStore]

type Continue = Function4[Set[Storable], BStore, Time, Cache, ValStore]

@@

def aval(e: Expr, env: Env, bstore: BStore, time: Time, cache: Cache, continue: Continue): ValStore = {
  val config = Config(e, env, bstore, time)
  if (cache.contains(config)) {
    val ValStore(vs, bstore, time) = cache(config)
    return continue(vs, bstore, time, cache)
  }
  val newTime = tick(config)
  e match {
    case Let(x, App(f, ae), e) if isAtomic(ae) =>
      val closures = aeval(f, env, bstore).toList

      def nd(closures: List[Storable], accds: Set[Storable], accbstore: BStore, acctime: Time, cache: Cache): ValStore  = {
        closures match {
          case Nil =>
            val baddr = allocBind(x, acctime)
            val newEnv = env + (x -> baddr)
            val newStore = accbstore.update(baddr, accds)
            aval(e, newEnv, newStore, acctime, cache, (ds: Set[Storable], accbstore: BStore, acctime: Time, accCache: Cache) => {
                val newCache = accCache + (Config(e, newEnv, newStore, acctime) -> ValStore(ds, accbstore, acctime))
                continue(ds, accbstore, acctime, newCache)
            })
          case Clos(Lam(v, body), env_c)::rest =>
            val baddr = allocBind(v, newTime)
            val newEnv = env_c + (v -> baddr)
            val newStore = accbstore.update(baddr, aeval(ae, env, bstore)) //TODO: which store?
            aval(body, newEnv, newStore, newTime, cache, (ds: Set[Storable], accbstore: BStore, acctime: Time, accCache: Cache) => {
                val newCache = accCache + (Config(body, newEnv, newStore, newTime) -> ValStore(ds, accbstore, acctime))
                nd(rest, ds++accds, accbstore, acctime, newCache)
            })
        }
      }

      nd(closures, Set(), bstore, newTime, cache)
    case ae if isAtomic(ae) =>
      val ds = aeval(ae, env, bstore)
      continue(ds, bstore, newTime, cache)
  }
}

def done: Continue = (ds: Set[Storable], bstore: BStore, time: Time, cache: Cache) => {
  ValStore(ds, bstore, time)
}
def analyze(e: Expr): ValStore = aval(e, Map(), Store[BAddr, Storable](Map()), List(), Map[Config, ValStore](), done)
\end{lstlisting}

>>>>

As we mentioned previously, the space of addresses is finite in AAM.
Binding addresses are parameterized by variable names and the time that creates this binding,
which are both finite.
Continuation addresses @KAddr@ has two variants: 
1) @Halt@ which corresponds to the empty stack, and
2) @ContAddr@ consists of the entry expressions of callee, which are also also
finite.
One may ask, why not also keep track of the time in continuation addresses?
(TODO: why target expression, allocation polyvariance)

@@

abstract class KAddr
case object Halt extends KAddr
case class ContAddr(tgt: Expr) extends KAddr
\end{lstlisting}

@@

\begin{lstlisting}
def allocBind(x: String, time: Time): BAddr = BAddr(x, time)
def allocKont(tgtExpr: Expr): KAddr = ContAddr(tgtExpr)
\end{lstlisting}

@@

\begin{lstlisting}
def step(s: State): List[State] = {
  val new_time = tick(s)
  s match {
    case State(Let(x, App(f, ae), e), env, bstore, kstore, kaddr, time) 
      if isAtomic(ae) =>
      val closures = atomicEval(f, env, bstore).toList
      for (Clos(Lam(v, body), env_c) <- closures) yield {
        val baddr = allocBind(v, new_time)
        val new_env = env_c + (v -> baddr)
        val new_bstore = bstore.update(baddr, atomicEval(ae, env, bstore))
        val new_kaddr = allocKont(body)
        val new_kstore = kstore.update(new_kaddr, Cont(Frame(x, e, env), kaddr))
        State(body, new_env, new_bstore, new_kstore, new_kaddr, new_time)
      }
    case State(ae, env, bstore, kstore, kaddr, time) 
      if isAtomic(ae) =>
      val conts = kstore(kaddr).toList
      for (Cont(Frame(x, e, env_f), f_kaddr) <- conts) yield {
        val baddr = allocBind(x, new_time)
        val new_env = env_f + (x -> baddr)
        val new_store = bstore.update(baddr, atomicEval(ae, env, bstore))
        State(e, new_env, new_store, kstore, f_kaddr, new_time)
      }
  }
}
\end{lstlisting}

@@

\begin{lstlisting}
case class P4FContAddr(tgt: Expr, tgtEnv: Env) extends KAddr
def allocKont(tgtExpr: Expr, tgtEnv: Env): KAddr = 
  P4FContAddr(tgtExpr, tgtEnv)
\end{lstlisting}

@@

\begin{lstlisting}
case class Config(e: Expr, env: Env, store: BStore, time: Time)
case class ValStore(ds: Set[Storable], store: BStore, time: Time)
type Cache = Map[Config, ValStore]

type Continue = Function2[ValStore, Cache, ValStore]

@@

def aval(e: Expr, env: Env, bstore: BStore, time: Time, cache: Cache, continue: Continue): ValStore = { 
  val config = Config(e, env, bstore, time)
  if (cache.contains(config)) {
    return continue(cache(config), cache)
  }   
  val newTime = tick(config)
  e match {
    case Let(x, App(f, ae), e) if isAtomic(ae) =>
      val closures = aeval(f, env, bstore).toList

      def nd(closures: List[Storable], accds: Set[Storable],
             accbstore: BStore, acctime: Time, cache: Cache): ValStore  = { 
        closures match {
          case Nil =>
            val baddr = allocBind(x, acctime)
            val newEnv = env + (x -> baddr)
            val newStore = accbstore.update(baddr, accds)
            aval(e, newEnv, newStore, acctime, cache, (vs: ValStore, accCache: Cache) => {
              val newCache = accCache + (Config(e, newEnv, newStore, acctime) -> vs) 
              continue(vs, newCache)
            })  
          case Clos(Lam(v, body), env_c)::rest =>
            val baddr = allocBind(v, newTime)
            val newEnv = env_c + (v -> baddr)
            val newStore = accbstore.update(baddr, aeval(ae, env, bstore)) //TODO: which store?
            aval(body, newEnv, newStore, newTime, cache, (vs: ValStore, accCache: Cache) => {
              val newCache = accCache + (Config(body, newEnv, newStore, newTime) -> vs) 
              nd(rest, vs.ds++accds, accbstore, acctime, newCache)
            })  
        }   
      }

      nd(closures, Set(), bstore, newTime, cache)
    case ae if isAtomic(ae) =>
      val ds = aeval(ae, env, bstore)
      continue(ValStore(ds, bstore, newTime), cache)
  }   
}

def done: Continue = (vs: ValStore, cache: Cache) => { vs }                                                                                                                                                                                                 
def analyze(e: Expr): ValStore = aval(e, Map(), Store[BAddr, Storable](Map()),
                                      List(), Map[Config, ValStore](), done)
\end{lstlisting}
